---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# taxonomy.tools

<!-- badges: start -->
[![R-CMD-check](https://github.com/Pakillo/taxonomy.tools/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Pakillo/taxonomy.tools/actions/workflows/R-CMD-check.yaml)
`r badger::badge_repostatus("Active")`
<!-- badges: end -->

taxonomy.tools is an R package to help working with taxonomic data. 

By now, it builds upon [rWCVP package](https://matildabrown.github.io/rWCVP) to match plant taxonomic names against the [World Checklist of Vascular Plants (WCVP)](https://powo.science.kew.org/about-wcvp).

## Installation

You can install the development version of taxonomy.tools from [R-universe](https://pakillo.r-universe.dev/taxonomy.tools):

``` r
install.packages("taxonomy.tools", repos = c("https://pakillo.r-universe.dev", "https://cloud.r-project.org"))
```

or from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("Pakillo/taxonomy.tools")
```

## Usage

```{r}
library(taxonomy.tools)
```

### Matching plant taxonomic names against WCVP

[wcvp_match_names_parallel](https://pakillo.github.io/taxonomy.tools/reference/wcvp_match_names_parallel.html) runs [rWCVP::wcvp_match_names](https://matildabrown.github.io/rWCVP/reference/wcvp_match_names.html) in parallel to speed up matching with large taxonomic lists.

```{r message=FALSE}

df <- data.frame(taxon = c("Laurus nobilis", "Laurus nobilis", "Laurus nobili"),
                 author = c(NA, "L.", NA))

out <- wcvp_match_names_parallel(df, 
                                 name_col = "taxon", 
                                 author_col = "author", 
                                 cores = 3)
```

```{r }
dplyr::glimpse(out)
```


## Citation

```{r}
citation("taxonomy.tools")
```

